ext_risk_copula

### 2019-01-16 ext_risk_copula.Rmd
fixed bug

rlist<-seq(from=1.5,to=7.5,by=0.5)
numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
K_e<-((r^(1/b))-1)/a
scl<-1
K<-K_e
ext_thrs<-K/10
rc<-((b/(b-1)))^b # critical value of r from monotonic to osc steady state approach transition

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc=2.73) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_hassell}](./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc=2.73) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_hassell}](./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf){ width=40%, height=40% }

@@

```{r fig_msmith_r_vary, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

rlist<-seq(from=1.1,to=1.9,by=0.2)
numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-4
K_e<-((r-1)^(1/b))/a
K<-K_e
scl<-1
ext_thrs<-K/10

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_local_disp_r_variation.pdf",heigh=3,width=15)
op<-par(mfrow=c(1,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="msmith",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for global dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_global_disp_r_variation.pdf",heigh=3,width=15)
op<-par(mfrow=c(1,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="msmith",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 0.5, b = 4, rc=1.5) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/ext_risk_copula/msmith_ext_risk_local_disp_r_variation.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 0.5, b=4, rc=1.5) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/ext_risk_copula/msmith_ext_risk_global_disp_r_variation.pdf){ width=40%, height=40% }

>>>>

rlist<-seq(from=1.5,to=7.5,by=0.5)
numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
scl<-1

rc<-((b/(b-1)))^b # critical value of r from monotonic to osc steady state approach transition

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf",heigh=9,width=15)
op<-par(mfrow=c(3,5),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="hassell",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_hassell}](./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Hassell model : a = 0.5, b = 100, rc = 2.73) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_hassell}](./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf){ width=40%, height=40% }

@@

```{r fig_msmith_r_vary_localdisp, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
rlist<-seq(from=1.2,to=2.8,by=0.2)
numsims<-10000
numsteps<-25
numlocs<-5
a<-1
b<-3
scl<-1

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_local_disp.pdf",heigh=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    K_e<-((r-1)^(1/b))/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="msmith",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for global dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_global_disp.pdf",heigh=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    K_e<-((r-1)^(1/b))/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model="msmith",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 1.7) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/ext_risk_copula/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 1.7) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/ext_risk_copula/msmith_ext_risk_global_disp.pdf){ width=40%, height=40% }
